\subsection{Effect of the reduced training set size}

Our extended training set contains roughly 8.7 million events. Combined with the fact that our \gls{nn} is quite large
as well (about 4.5 million learnable parameters), the training takes a long time. We have thus decided to investigate
the effect of the reduced training set size on the performance of the classifier.

We have performed 5 experiments with 100\%, 80\%, 60\%, 40\%, and 20\% of the extended training set. The results are
shown in \autoref{tab:reduced_training_set}. During each experiment, we have kept the same random seed to keep the
initialization of the \gls{nn} the same. We also kept the same batch size and learning rate. The results show that the
performance of the classifier do not degrade dramatically between 100\% and 80\% of the training set. Even 60\%-40\%
provide good compromise between training time and performance. Such training set size of about 4 million events seem
adequate to obtain some sufficiently good results. Of course, for maximum performance, it is best to use the full
training set. When dropping to 20\% of the training set, the performance degrades significantly and does not accurately
represent the full potential of the model.

\begin{table}[htbp]
    \centering
    \begin{tabular}{rrr}
        \toprule
        \textbf{Training Set Size (\%)} & \textbf{Accuracy (\%)} & \textbf{Training Time per 100 Epochs} \\
        \midrule
        100                             & 95.2                   & 20 minutes                            \\
        80                              & 94.8                   & 16.7 minutes                          \\
        60                              & 93.5                   & 13.3 minutes                          \\
        40                              & 91.2                   & 10 minutes                            \\
        20                              & 87.3                   & 6.7 minutes                           \\
        \bottomrule
    \end{tabular}
    \caption{Effect of reduced training set size on classifier performance}
    \label{tab:reduced_training_set}
\end{table}
